\documentclass{article}

% dependencies
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}

% style
\geometry{margin = 48pt}

\definecolor{seagreen}{HTML}{A1BF49}
\definecolor{wowgreen}{HTML}{E5FF63}

\titleformat{\section}
    {\color{seagreen}\normalfont\Large\bfseries}
    {\thesection}{1pt}{}[{\titlerule[0.5pt]}]

\hypersetup{
    colorlinks = true,
    urlcolor = seagreen,
    allbordercolors = wowgreen
}

\setstretch{0.85}

\pretitle{\begin{flushleft}\huge\bfseries}
\posttitle{\end{flushleft}}

\title{
    \vspace{-48pt}
    \textbf{Nick Kunz}
    \vspace{-56pt}
}
\date{}

\pagenumbering{gobble}

% text
\begin{document}
\maketitle
\noindent
Address: \space\space 602 Rhodes Hall, Ithaca, NY 14853\\
% Office: \space\space\space +1 $($607$)$ 255-4756\newline
Mobile: \space\space\space +1 $($602$)$ 710-8608\newline
Email: \space\space\space\space\url{nick.kunz@me.com}\newline
Website: \space\space\url{nickkunz.com}
    \section*{Education}
        \textbf{Cornell University} | Ithaca, NY\hfill{2026}\newline
        Ph.D., Systems Engineering\newline
        \textit{Advisor: H. Oliver Gao}\newline\newline
        \textbf{Columbia University} | New York, NY\hfill{2019}\newline
        M.S., Urban Planning, Urban Analytics\newline
        \textit{Advisors: Lance Freeman, Kazuki Sakamoto}\newline\newline
        \textbf{Harvard University} | Cambridge, MA\hfill{2012}\newline
        Urban Planning\newline
        \textit{Advisor: Nick Hornig}\newline\newline
        \textbf{Arizona State University} | Tempe, AZ\hfill{2012}\newline
        B.S. $($Hons.$)$, \textit{summa cum laude}, Housing \& Urban Development\newline
        \textit{Advisors: Kevin Kellogg, Michael Underhill, Trevor Barger}
    \section*{Research}
    \subsection*{Journal Articles}
        \textbf{N. Kunz}, H. O. Gao, ``Global Geolocated Realtime Data of Interfleet Urban Transit Bus Idling'' \textit{In Preparation.} 2024.
    \subsection*{Conference Proceedings}
        W. Wu, \textbf{N. Kunz}, P. Branco, ``ImbalancedLearningRegression'' in \textit{Machine Learning and Knowledge Discovery in Databases: European Conference, ECML PKDD, September 19–23, 2022, Grenoble, France,} Proceedings, Part VI, Lecture Notes in Computer Science, vol 13718. Springer, pp. 645–648, 2023.\space\href{https://doi.org/10.1007/978-3-031-26422-1}{\texttt{[Link]}}
    \subsection*{Industry Research}
        N. Kunz, ``n-Dimensional Mapping by Normalized Value Approximation: Squad Immersive Virtual Trainer (SiVT) Safety Performance Metrics,'' Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2021. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        N. Kunz, ``Normalized n-Dimensional Inverse Euclidean Distance: Combining Independent Performance Metrics,'' Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2021. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        % N. Kunz, ``Minimum-Weighted Mean Variability: Within Group Performance Metrics,'' Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2020. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        N. Kunz, ``An Exploratory Data Analysis of the Gavin Cup: Brining Readiness \& Performance Metrics Into Focus,'' Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2020. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.
    \subsection*{Theses}
        N. Kunz, ``Unsupervised Learning for Submarket Modeling: A Proxy for Neighborhood Change,'' M.S. Thesis, Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile: Columbia Academic Commons.\space\href{https://doi.org/10.7916/d8-rj87-yx32}{\texttt{[Link]}}\newline\newline
        N. Kunz, ``Realizing Interactive Architecture: A Driver of the Knowledge Economy,'' B.S. $($Hons.$)$ Thesis, Barrett, The Hons. Col., Arizona State Univ., Tempe, AZ, 2012. [Online]. Availabile: Barrett, The Honors College Thesis/Creative Project Collection.\space\href{https://repository.asu.edu/collections/130}{\texttt{[Link]}}
\newpage
    \section*{Industry Experience}
        \textbf{Deloitte} | Seattle, WA\hfill{2021 - 2024}\newline
        Senior Data Scientist\newline\newline
        % \textit{Artificial Intelligence \& Data}\space\href{https://www2.deloitte.com/be/en/pages/strategy-operations/strategy-analytics-mergers-acquisitions/topics/analytics-and-cognitive.html}{\texttt{[Link]}}\newline\newline
        \textbf{Microsoft} | Redmond, WA\hfill{2020 - 2021}\newline
        Data Scientist\newline\newline
        % \textit{Integrated Visual Augmentation System}\space\href{https://news.microsoft.com/transform/u-s-army-to-use-hololens-technology-in-high-tech-headsets-for-soldiers/}{\texttt{[Link]}}\newline\newline
        \textbf{Pacific Prospecting Group} | Seattle, WA\hfill{2017 - 2019}\newline
        Data Scientist\newline\newline
        % \textit{Cryptocurrency Mining \& Management}\space\href{http://pacificprospectinggroup.com}{\texttt{[Link]}}\newline\newline
        \textbf{Brawner \& Company} | Snoqualmie, WA\hfill{2016 - 2017}\newline
        Development Analyst\newline\newline
        % \textit{Real Estate Development}\space\href{https://jhbrawner.com}{\texttt{[Link]}}\newline\newline
        \textbf{bcWORKSHOP} | Dallas, TX\hfill{2013 - 2014}\newline
        Fellow
        % \textit{Architecture \& Planning}\space\href{https://www.bcworkshop.org}{\texttt{[Link]}}
    \section*{Software Packages}
        % \textbf{PUPHL: Proximal Policy Optimization Utilizing Pseudo-Huber Loss}\hfill{2021}\newline
        % \faGithub\space Github [ \href{https://github.com/nickkunz/puphl}{\texttt{Link}} ]\newline\newline
        % A modified Proximal Policy Optimization (PPO) policy gradient algorithm. Applies Pseudo-Huber Loss to the critic loss function in place of traditional Mean Squared Error (MSE). Adds additional critic loss function constraint $\delta$ in an effort to further reduce variance to PPO and future policy gradient methods. \textit{Currently in development.}\newline\newline
        \textbf{SMOGN: Synthetic Minority Over-Sampling Technique for Regression with Gaussian Noise}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/smogn}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/smogn}{\texttt{Link}} ]\space\faUsers\space Kaggle [ \href{https://www.kaggle.com/aleksandradeis/regression-addressing-extreme-rare-cases}{\texttt{Link}} ]\space\faStackExchange\space Stack Exchange [ \href{https://datascience.stackexchange.com/questions/39232/how-to-make-multiple-regression-perform-better-for-outliers-without-reducing-e/64933#64933}{\texttt{Link}} ]\newline\newline
        A novel pre-processing algorithm designed to address imbalanced data for regression problems. Conducts over-sampling with traditional interpolation, as well as with the introduction of Gaussian noise. Selects between the two over-sampling techniques by the KNN distances underlying a given observation.\newline\newline
        \textbf{NestedHyperBoost: Nested Cross-Validation for Bayesian Optimized Gradient Boosting}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/nestedhyperboost}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/nestedhyperboost}{\texttt{Link}} ]\newline\newline
        Unifies Nested K-Fold Cross-Validation, Bayesian Hyperparameter Optimization, and Gradient Boosting. Designed for rapid prototyping on small to mid-sized data sets. Quickly obtains high quality prediction results by abstracting away tedious hyperparameter tuning and implementation details in favor of usability and implementation speed.\newline\newline
        \textbf{NestedHyperLine: Nested Cross-Validation for Bayesian Optimized Linear Regularization}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/nestedhyperline}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/nestedhyperline}{\texttt{Link}} ]\newline\newline
        Unifies Nested K-Fold Cross-Validation, Bayesian Hyperparameter Optimization, and Linear Regularization. Designed for rapid prototyping on small to mid-sized data sets. Quickly obtains high quality prediction results by abstracting away tedious hyperparameter tuning and implementation details in favor of usability and implementation speed.\newline\newline
        \textbf{CRASSMAT: Conditional Random Sampling Sparse Matrices}\hfill{2019}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/crassmat}{\texttt{Link}} ] \space\faRProject\space CRAN\space [ \href{https://cran.r-project.org/web/packages/crassmat/crassmat.pdf}{\texttt{Link}} ]\newline\newline
        A novel matrix sampling algorithm designed to conditionally random sample sparse matrices. Useful for training and test set splitting prior to model fitting in cross-validation procedures and for estimating the predictive accuracy of imputation methods, such as Matrix Factorization, Non-Negative Matrix Factorization (NNMF), and Singular Value Decomposition (SVD).
    \section*{Selected Projects}
        \textbf{N. Kunz}, S. Huang, S. Osakata, ``Cloudy Night: Activating Park Space by Illuminated Interactivity," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/7502-cloudy-night}{\texttt{Link}} ]\space\faGithub\space Github [ \href{https://github.com/nickkunz/cloudynight}{\texttt{Link}} ]\space\space \faYoutube\space YouTube [ \href{https://www.youtube.com/watch?v=GWaXrN79Lbw&feature=emb_title}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://edblogs.columbia.edu/plana6102-001-2019-1/2019/05/10/cloudy-night-activating-park-space-by-illuminated-interactivity-2/}{\texttt{Link}} ]\newline\newline
        \textbf{N. Kunz} and S. Bhele, ``Signal or Noise? Qualified Opportunity Zone Affect on Development Activity in Queens," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://cdn.filepicker.io/api/file/guXiVLU6QreQgKPPPUG8?&fit=max}{\texttt{Link}} ]\space\faGithub\space Github [ \href{https://github.com/nickkunz/queens-dbscan}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/queens_report}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://www.leahmeisterlin.com/advanced-spatial-analysis-2019}{\texttt{Link}} ]\newline\newline
        E. Hudgins and \textbf{N. Kunz}, ``Planning for Extreme Settlements, McMurdo Station, Antarctica," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2018. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/5461}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/mcmurdo}{\texttt{Link}} ]\newline\newline
        J. Karasik, S. Lee, \textbf{N. Kunz}, \textit{et. al.} ``Negotiating Fragments (Restructuring Quarto Workshop)," Genoa, Italy, Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2018. [Online]. Available:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/courses/87029-1878-genoa-italy-negotiating-fragments}{\texttt{Link}} ]\space\faYoutube\space YouTube [ \href{https://www.youtube.com/watch?v=NaVhil1sQfY}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/geotagged_genoa}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/quarto}{\texttt{Link}} ]\space\faNewspaper\space Press [ \href{http://www.comune.genova.it/content/restructuring-quarto-workshop-le-idee-degli-studenti-della-columbia-university-l39ex-op}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Proportionalities: A Decade of Housing Markets to Subway Stations in Manhattan from 2006 to 2016," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Available:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4836}{\texttt{Link}} ]\space\faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4835}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/gis}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://www.leahmeisterlin.com/teaching#/gis-2017-2018/}{\texttt{Link}} ]\newline\newline
        % N. Kunz, ``Reimaged: John Snow's Cholera Map of 1854, ``Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Available:\newline\newline
        % \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/reimagined}{\texttt{Link}} ]\newline\newline
        G. S. Coch, S. Nelsen, \textbf{N. Kunz}, K. Warner, ``Seeking Refuge: The Geography of Migrant Deaths Along the US-MX Border," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4895}{\texttt{Link}} ]\space\faMedium\space Medium [ \href{https://medium.com/data-mining-the-city/seeking-refuge-the-geography-of-migrant-deaths-near-the-us-mx-border-b0f8f8be84ec}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Traditional Theory and the Historic Preservation of Singapore in the Period of the 1980's," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/singapore}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Health \& Wellness Alliance for Children: Children's Asthma, Healthy Physical Environments," Dallas County, Texas, bcWORKSHOP, Dallas, TX, 2014. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/asthma}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``The Bexar Street Corridor: A Century in Development," Dallas, Texas, bcWORKSHOP, Dallas, TX, 2013. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/bexar_present}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/bexar}{\texttt{Link}} ]\space\faHome\space bc [ \href{https://www.bcworkshop.org/posts/bexar-street-corridor}{\texttt{Link}} ]\space\faVimeo\space Vimeo [ \href{https://vimeo.com/81649797}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Fenway-Kenmore Square: Comprehensive Planning \& Finance," Cambridge, Massachusetts, Grad. Sch. of Design (GSD), Harvard Univ., Cambridge, MA, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/fenway_kenmore}{\texttt{Link}} ]\newline\newline
        % N. Kunz, ``Design Representation: Analog Modeling \& Hand Drafting," Grad. Sch. of Design (GSD), Harvard Univ., Cambridge, MA, 2012. [Online]. Availabile:\newline\newline
        % \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/design_rep}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Danelle Plaza: Complete Street Mobility Planning," Tempe, Arizona, Herberger Inst. for Des. and the Art., Arizona State Univ., Tempe, AZ, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/danelle_plaza}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Ascension: Multifamily Mixed-Use Real Estate Development Proposal," Tempe, Arizona, n Creative Studios, Phoenix, AZ, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/ascension}{\texttt{Link}} ]\newline\newline
        N. Kunz, ``Sui Residence: Second Story Architectural Design," Paradise Valley, Arizona, n Creative Studios, Phoenix, AZ, 2011. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/sui}{\texttt{Link}} ]
    \section*{Honors \& Awards}
        \textbf{Graduate Engineering Fellowship}, Cornell University | Ithaca, NY\hfill{2023 - 2026}\newline
        \textbf{Systems Engineering Fellowship}, Cornell University | Ithaca, NY\hfill{2022 - 2023}\newline
        \textbf{Top 20 Analytics Libraries}, Github20k | San Francisco, CA\hfill{2023}\newline
        \textbf{AVID Applause Award}, Deloitte Consulting | Seattle, WA\hfill{2022}\newline %% 06/14/2022, Number: 1321982
        \textbf{Distinguished Alumni Award}, Arizona State University | Tempe, AZ\hfill{2016}\newline
        \textbf{Eli Segal AmeriCorps Education Award}, AmeriCorps | Dallas, TX\hfill{2014}\newline
        \textbf{Dingwall Foundation Scholarship}, William Orr Dingwall Foundation | Washington, DC\hfill{2011 - 2012}\newline
        \textbf{Barrett, The Honors College Scholarship}, Arizona State University | Tempe, AZ\hfill{2010 - 2012}\newline
        \textbf{AIERF Undergraduate Scholarship}, Appraisal Institute | Chicago, IL\hfill{2010 - 2011}\newline
        \textbf{Herberger Institute for Design \& the Arts Scholarship}, Arizona State University | Tempe, AZ\hfill{2010}\newline
        \textbf{Study.net Foundation Scholarship}, Study.net | Fort Lauderdale, FL\hfill{2010}\newline
        \textbf{Dean's List} \textit{(4.00/4.00 GPA)}, Arizona State University | Tempe, AZ\hfill{2009 - 2012}
        \section*{Mentorship Activities}
        \textbf{Albert Rosario-Pichardo}, M.S., Urban Analytics, Columbia University | New York, NY\hfill{2023 - Present}\newline
        GIS Analyst Intern, New York City Economic Development Corporation\newline
        \textit{Academic and professional development in early career public service.}\newline\newline
        \textbf{Albert Ruiz Martinez}, B.S., Computer Science, Arizona State University | Tempe, AZ\hfill{2023 - 2024}\newline
        Analyst, Deloitte Consulting\newline
        \textit{Professional development and management in early career consulting.}\newline\newline
        \textbf{Julia VanPutte}, B.S., Operations Research, Cornell University | Ithaca, NY\hfill{2022 - 2024}\newline
        Business Intelligence Engineer Intern, Amazon\newline
        \textit{Academic and professional development from undergraduate school to industry.}\newline\newline
        \textbf{Chawner Hurd}, M.B.A., Business, Columbia University | New York, NY\hfill{2020 - 2023}\newline
        Associate Intern, Visa\newline
        \textit{Military transition from US Army, 5th Special Forces Group to graduate school and industry.}\newline\newline
        \textbf{Michael Bollinger}, B.A., Computer Science, Columbia University | New York, NY\hfill{2019 - 2023}\newline
        Software Engineer Intern, Amazon\newline
        \textit{Military transition from US Army, 75th Ranger Regiment to undergraduate school and industry.}\newline\newline
        \textbf{Daniel Hineline}, B.A., Political Science, Columbia University | New York, NY\hfill{2018 - 2023}\newline
        Associate Intern, Guggenheim Partners\newline
        \textit{Military transition from US Army, 82nd Airborne Division to undergraduate school and industry.}
    \section*{Talks, Exhibits \& Presentations}
        \textbf{Global Geolocated Realtime Data}, Gao Labs Flash Talks, Cornell University | Ithaca, NY\hfill{2023}\newline
        \textbf{Emerging Technology Workshop}, Countryside Angels Talks, Ag Ventures Alliance | Mason City, IA\hfill{2021}\newline
        \textbf{Urban Planners in Technology}, Alumni Panel, Columbia University | New York, NY\hfill{2021}\newline
        \textbf{Cloudy Night}, Urban Planning Showcase, Columbia University | New York, NY\hfill{2019}\newline
        \textbf{The Bexar Street Corridor}, US Congrasswoman Eddie Bernice Johnson's Office | Dallas, TX\hfill{2014}\newline
        \textbf{The Bexar Street Corridor}, TR Hoover Community Development Corporation | Dallas, TX\hfill{2014}\newline
        \textbf{The Bexar Street Corridor}, bcSHOPFRONT Series, bcWORKSHOP| Dallas, TX\hfill{2013}\newline
        \textbf{Realizing Interactive Architecture}, Honors Symposium, Arizona State University | Tempe, AZ\hfill{2012}
    \section*{Media \& Press}
        \textbf{Spotlights: Nick Kunz}, Cornell Systems Engineering, Cornell University | Ithaca, NY \href{https://www.systemseng.cornell.edu/spotlights/nick-kunz-dont-be-afraid-ask-questions}{\texttt{[Link]}} \hfill{2023}\newline
        \textbf{Meet the N-K Alumni Nick Kunz}, Northwood Anchor, Vol. 126, No. 41, Pg. 4 | Northwood, IA \href{http://nwdanchor.com/sites/default/files/2022anchor41.pdf}{\texttt{[Link]}} \hfill{2022}\newline
        \textbf{Achievement Oriented: Nick Kunz}, ASU Magazine, Vol. 20, No. 2, Pg. 7| Tempe, AZ\space \href{https://news.asu.edu/sites/default/files/december_2016.pdf}{\texttt{[Link]}} \hfill{2016}\newline
        \textbf{Welcome Nick Kunz}, bcWORKSHOP | Dallas, TX\space \href{https://www.bcworkshop.org/posts/welcome-nick-kunz}{\texttt{[Link]}} \hfill{2013}
    \section*{Military Service}
    \subsection*{Assignments}
        \textbf{US Army, 2d Ranger Battalion, 75th Ranger Regiment} | Fort Lewis, WA \hfill{2015 - 2016}\newline
        \textit{Infantry}\newline\newline
        \textbf{US Army, Ranger Training Detachment} | Fort Benning, GA \hfill{2015}\newline
        \textit{Ranger Assessment and Selection Program}\newline\newline
        \textbf{US Army, 1st Special Warfare Training Group} | Fort Bragg, NC \hfill{2014}\newline
        \textit{Special Forces Assessment and Selection}\newline\newline
        \textbf{US Army, 1st Special Warfare Training Group} | Fort Bragg, NC \hfill{2014}\newline
        \textit{Special Forces Preparation and Conditioning}\newline\newline
        \textbf{US Army, 507th Parachute Infantry Regiment} | Fort Benning, GA \hfill{2014}\newline
        \textit{Airborne School}\newline\newline
        \textbf{US Army, 19th Infantry Regiment} | Fort Benning, GA \hfill{2014}\newline
        \textit{Infantry School}
\newpage
    \subsection*{Decorations}
        \textbf{Expert Badge, Rifle Component Bar}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2016}\newline
        \textbf{Global War on Terrorism Service Medal}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2016}\newline
        \textbf{Driver Badge, Wheeled Vehicle Component Bar}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2015}\newline
        \textbf{Parachutist Badge, Unit Trimming}, US Army, 507th Parachute Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{Infantry Blue Chord Fourragère}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{National Defense Service Medal}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{Army Service Ribbon}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}
    \section*{Civil Service}
        \textbf{AmeriCorps} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Volunteer in Service to America (VISTA)}\newline\newline
        \textbf{Open Architecture Collaborative} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Architecture \& Planning}\newline\newline
        \textbf{Trinity Park Conservancy} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Public Park Conservation}
    \section*{Technical Skills}
    \subsection*{Languages}
        \textbf{Scripting}: Python, Bash\newline
        \textbf{Statistical}: R, Stata\newline
        \textbf{Compiled}: C/C++, Fortran\newline
        \textbf{Database}: SQL, NoSQL, Cypher\newline
        \textbf{Typesetting}: \LaTeX, Markdown
    \subsection*{Frameworks}
        \textbf{Data Science}: NumPy, SciPy, Pandas, statsmodels, Featuretools, Tidyverse\newline
        \textbf{Visualization}: Matplotlib, Seaborn, Plotly, Processing, Shiny, ggplot\newline
        \textbf{Statistical Learning}: Scikit-Learn, XGBoost, LightGBM, CatBoost\newline
        \textbf{Reinforcement Learning}: OpenAI Baselines, Stable Baselines\newline
        \textbf{Prompt Engineering}: GPT, LLaMa, Claude\newline
        \textbf{Deep Learning}: Pytorch, TensorFlow, ONNX
    \subsection*{Deployment}
        \textbf{DevOps}: Git, Ubuntu, Docker, CI/CD\newline
        \textbf{Databases}: PostgreSQL, SQLite, CosmosDB, Neo4j\newline
        \textbf{Web Services}: Flask, Gunicorn, Nginx\newline
        \textbf{Web Automation}: Selenium, Puppeteer\newline
        \textbf{Cloud Platforms}: Azure, AWS, Databricks\newline
        \textbf{Security}: OWASP ZAP, STIGs
    \subsection*{Software}
        \textbf{Development Environments}: VS Code, RStudio, Jupyter\newline
        \textbf{Geographic Information Systems}: ArcGIS, QGIS, OSM, Leaflet, Mapbox\newline
        \textbf{3D Modeling \& Optimization}: Rhino, Grasshopper, SketchUp, AutoCAD, Unity\newline
        \textbf{Design \& Illustration}: Adobe Photoshop, Illustrator, InDesign\newline
        \textbf{Financial Modeling}: Excel, Macros, CoStar\newline
        \textbf{Studio \& Live Audio}: Logic, Protools
    \subsection*{Prototyping}
        \textbf{Sensors \& Hardware}: Arduino, Raspberry Pi\newline
        \textbf{Project Management}: Agile, Scrum, Critical Path\newline
        \textbf{Electrical}: Soldering, Wiring, Safety\newline
        \textbf{Ideation}: Drawing \& Sketching, Storyboarding\newline
        \textbf{Analogs}: Hand Drafting, Physical Modeling, Photography
\newpage
    \section*{Personal Activities}
    \subsection*{Music \& Live Audio}
        \textbf{Atlas North American Tour} | US \& Canada\hfill{2013}\newline
        The Word Alive \textit{(Fearless Records)}, Co-Tour Manager\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline\newline
        \textbf{Fight the Silence Tour} | US\hfill{2013}\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline
        For Today \textit{(Razor \& Tie Records)}, Guitar Tech\newline\newline
        \textbf{All Stars Tour} | US\hfill{2012}\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline
        A Skylit Drive \textit{(Fearless Records)}, Guitar Tech\newline\newline
        \textbf{Van's Warped Tour} | US \& Canada\hfill{2011}\newline
        The Word Alive \textit{(Fearless Records)}, Co-Tour Manager\newline
        Of Mice \& Men \textit{(Rise Records)}, Guitar Tech\newline\newline
        \textbf{Regional Performances} | US\hfill{2011}\newline
        The Rendering \textit{(Authentik Artists)}, Guitar
    \subsection*{Outdoors \& Endurance}
        Running \textit{(Half Marathon, 13.1mi, Marathon, 26.2mi)}\newline
        Cycling \textit{(Century Ride, 100mi)}\newline
        Hiking \textit{(Mt. Rainier, Mt. Olympus, Mt. Denali)}\newline
        Overlanding \textit{(Rubicon Trail, Alaskan Arctic Circle, Powder River Basin, All 50 States)}\newline
        Snowboarding \textit{(Cascades, Sierra Nevadas, Colorado Plateau, Mississippi River Valley)}\newline
        \mbox{}
        \vfill
        \hfill{}\textit{Updated: Feb. 2024}
\end{document}