\documentclass{article}

% dependencies
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}

% style
\geometry{margin = 48pt}

\definecolor{seagreen}{HTML}{A1BF49}
\definecolor{wowgreen}{HTML}{E5FF63}

\titleformat{\section}
    {\color{seagreen}\normalfont\Large\bfseries}
    {\thesection}{1pt}{}[{\titlerule[0.5pt]}]

\hypersetup{
    colorlinks = true,
    urlcolor = seagreen,
    allbordercolors = wowgreen
}

\setstretch{0.88}

\pretitle{\begin{flushleft}\huge\bfseries}
\posttitle{\end{flushleft}}

\title{
    \vspace{-48pt}
    \textbf{Nick Kunz}
    \vspace{-56pt}
}
\date{}

\pagenumbering{gobble}

% text
\begin{document}
    \maketitle
    \subsection*{\textit{Data Scientist}}
        Location: \space\space\space Seattle, WA\newline
        Mobile: \space\space\space\space\space+1 $($602$)$ 710-8608\newline
        Email: \space\space\space\space\space\space\url{nick.kunz@me.com}\newline
        Website: \space\space\space\space\url{nickkunz.com}
    % \section*{Research Interests}
        % \textbf{Domains}: Cyber-Physical Systems, Urban Informatics, Urban Mobility, Housing Affordability\newline
        % \textbf{Methods}: Reinforcement Learning, Unsupervised Learning, Statistics, Geographic Information Systems (GIS)\newline
        % \textbf{Sources}: Sensors \& Devices, Synthetic Data, Open Data, Social Media, Demographics, Market \& Economics
    \section*{Education}
        \textbf{Columbia University} | New York, NY\hfill{2019}\newline
        Master of Science, Urban Planning, Urban Analytics\newline
        \textit{Advisors: Lance Freeman, Kazuki Sakamoto}\newline\newline
        \textbf{Harvard University} | Cambridge, MA\hfill{2012}\newline
        Non-Degree, Urban Planning\newline
        \textit{Advisor: Nick Hornig}\newline\newline
        \textbf{Arizona State University} | Tempe, AZ\hfill{2012}\newline 
        Bachelor of Science in Design $($Hons.$)$, \textit{summa cum laude}, Housing \& Urban Development\newline
        \textit{Advisors: Kevin Kellog, Michael Underhill, Trevor Barger}
    \section*{Research}
    \subsection*{Theses}
        N. Kunz, "Unsupervised Learning for Submarket Modeling: A Proxy for Neighborhood Change," M.S. Thesis, Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile: Columbia Academic Commons.\space\href{https://doi.org/10.7916/d8-rj87-yx32}{\texttt{[Link]}}\newline\newline
        N. Kunz, "Realizing Interactive Architecture: A Driver of the Knowledge Economy," B.S.D. (Hons.) Thesis, Barrett, The Hons. Col., Arizona State Univ., Tempe, AZ, 2012. [Online]. Availabile: Barrett, The Honors College Thesis/Creative Project Collection.\space\href{https://repository.asu.edu/collections/130}{\texttt{[Link]}}
    \subsection*{Industry}
        N. Kunz, "n-Dimensional Mapping by Normalized Value Approximation: Squad Immersive Virtual Trainer (SiVT) Safety Performance Metrics," Squad Performance Metrics (SPM), Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2021. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        N. Kunz, "Normalized n-Dimensional Inverse Euclidean Distance: Combining Independent Performance Metrics," Squad Performance Metrics (SPM), Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2021. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        N. Kunz, "Minimum-Weighted Mean Variability: Within Group Performance Metrics," Squad Performance Metrics (SPM), Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2020. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.\newline\newline
        N. Kunz, "An Exploratory Data Analysis of the Gavin Cup: Brining Readiness \& Performance Metrics Into Focus," Squad Performance Metrics (SPM), Integrated Visual Augmentation System (IVAS), Microsoft, Redmond, WA, 2020. Protected from public disclosure pursuant to: Trade Secrets Act 18 USC § 1905, 5 USC § 552(b)(4), and C3.2.1.4. of US Dept. of Defense Regulation 5400.7-R. DISTRIBUTION F.
\newpage
    \section*{Industry Experience}
        \textbf{Microsoft} |Redmond, WA\hfill{2020 - 2021}\newline
        Data Scientist\newline
        \textit{Integrated Visual Augmentation System (IVAS)}\space\href{https://news.microsoft.com/transform/u-s-army-to-use-hololens-technology-in-high-tech-headsets-for-soldiers/}{\texttt{[Link]}}\newline\newline
        \textbf{Pacific Prospecting Group} | Seattle, WA\hfill{2017 - 2019}\newline
        Data Scientist\newline
        \textit{Computational Finance \& Engineering}\space\href{http://pacificprospectinggroup.com}{\texttt{[Link]}}\newline\newline
        \textbf{Brawner \& Company} | Snoqualmie, WA\hfill{2016 - 2017}\newline
        Development Analyst\newline
        \textit{Real Estate Development \& Finance}\space\href{https://jhbrawner.com}{\texttt{[Link]}}\newline\newline
        \textbf{bcWORKSHOP} | Dallas, TX\hfill{2013 - 2014}\newline
        Design Fellow\newline
        \textit{Architecture, Planning \& Policy}\space\href{https://www.bcworkshop.org}{\texttt{[Link]}}\newline\newline
        \textbf{n Creative Studios} | Phoenix, AZ\hfill{2011 - 2012}\newline
        Design Consultant\newline
        \textit{Real Estate Development}
    \section*{Software Packages}
        \textbf{PUPHL: Proximal Policy Optimization Utilizing Pseudo-Huber Loss}\hfill{2021}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/puphl}{\texttt{Link}} ]\newline\newline
        A modified Proximal Policy Optimization (PPO) policy gradient algorithm. Applies Pseudo-Huber Loss to the critic loss function in place of traditional Mean Squared Error (MSE). Adds additional critic loss function constraint $\delta$ in an effort to further reduce variance to PPO and future policy gradient methods. \textit{Currently in development.}\newline\newline
        \textbf{SMOGN: Synthetic Minority Over-Sampling Technique for Regression with Gaussian Noise}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/smogn}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/smogn}{\texttt{Link}} ]\space\faUsers\space Kaggle [ \href{https://www.kaggle.com/aleksandradeis/regression-addressing-extreme-rare-cases}{\texttt{Link}} ]\space\faStackExchange\space Stack Exchange [ \href{https://datascience.stackexchange.com/questions/39232/how-to-make-multiple-regression-perform-better-for-outliers-without-reducing-e/64933#64933}{\texttt{Link}} ]\space\faStackOverflow\space Stack Overflow [ \href{https://stats.stackexchange.com/questions/432185/oversampling-methods-for-numerical-data-regression/434216#434216}{\texttt{Link}} ]\newline\newline
        A novel pre-processing algorithm designed to address imbalanced data for regression problems. Conducts over-sampling with traditional interpolation, as well as with the introduction of Gaussian noise. Selects between the two over-sampling techniques by the KNN distances underlying a given observation.\newline\newline
        \textbf{NestedHyperBoost: Nested Cross-Validation for Bayesian Optimized Gradient Boosting}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/nestedhyperboost}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/nestedhyperboost}{\texttt{Link}} ]\newline\newline
        Unifies Nested K-Fold Cross-Validation, Bayesian Hyperparameter Optimization, and Gradient Boosting. Designed for rapid prototyping on small to mid-sized data sets. Quickly obtains high quality prediction results by abstracting away tedious hyperparameter tuning and implementation details in favor of usability and implementation speed.\newline\newline
        \textbf{NestedHyperLine: Nested Cross-Validation for Bayesian Optimized Linear Regularization}\hfill{2020}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/nestedhyperline}{\texttt{Link}} ] \space\faPython\space PyPI\space [ \href{https://pypi.org/project/nestedhyperline}{\texttt{Link}} ]\newline\newline
        Unifies Nested K-Fold Cross-Validation, Bayesian Hyperparameter Optimization, and Linear Regularization. Designed for rapid prototyping on small to mid-sized data sets. Quickly obtains high quality prediction results by abstracting away tedious hyperparameter tuning and implementation details in favor of usability and implementation speed.\newline\newline
        \textbf{CRASSMAT: Conditional Random Sampling Sparse Matrices}\hfill{2019}\newline
        \faGithub\space Github [ \href{https://github.com/nickkunz/crassmat}{\texttt{Link}} ] \space\faRProject\space CRAN\space [ \href{https://cran.r-project.org/web/packages/crassmat/crassmat.pdf}{\texttt{Link}} ]\newline\newline
        A novel matrix sampling algorithm designed to conditionally random sample sparse matrices. Useful for training and test set splitting prior to model fitting in cross-validation procedures and for estimating the predictive accuracy of imputation methods, such as Matrix Factorization, Non-Negative Matrix Factorization (NNMF), and Singular Value Decomposition (SVD).
\newpage
    \section*{Selected Projects}
        \textbf{N. Kunz}, S. Huang, and S. Osakata, "Cloudy Night: Activating Park Space by Illuminated Interactivity," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/7502-cloudy-night}{\texttt{Link}} ]\space\faGithub\space Github [ \href{https://github.com/nickkunz/cloudynight}{\texttt{Link}} ]\space\space \faYoutube\space Youtube [ \href{https://www.youtube.com/watch?v=GWaXrN79Lbw&feature=emb_title}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://edblogs.columbia.edu/plana6102-001-2019-1/2019/05/10/cloudy-night-activating-park-space-by-illuminated-interactivity-2/}{\texttt{Link}} ]\newline\newline
        \textbf{N. Kunz} and S. Bhele, "Signal or Noise? Qualified Opportunity Zone Affect on Development Activity in Queens," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2019. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://cdn.filepicker.io/api/file/guXiVLU6QreQgKPPPUG8?&fit=max}{\texttt{Link}} ]\space\faGithub\space Github [ \href{https://github.com/nickkunz/queens-dbscan}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/queens_report}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://www.leahmeisterlin.com/advanced-spatial-analysis-2019}{\texttt{Link}} ]\newline\newline
        E. Hudgins and \textbf{N. Kunz}, "Planning for Extreme Settlements, McMurdo Station, Antarctica," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2018. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/5461}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/mcmurdo}{\texttt{Link}} ]\newline\newline
        J. Karasik, S. Lee, \textbf{N. Kunz}, et. al. "Negotiating Fragments (Restructuring Quarto Workshop), Genoa, Italy," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2018. [Online]. Available:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/courses/87029-1878-genoa-italy-negotiating-fragments}{\texttt{Link}} ]\space\faYoutube\space Youtube [ \href{https://www.youtube.com/watch?v=NaVhil1sQfY}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/geotagged_genoa}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/quarto}{\texttt{Link}} ]\space\faNewspaper\space Press [ \href{http://www.comune.genova.it/content/restructuring-quarto-workshop-le-idee-degli-studenti-della-columbia-university-l39ex-op}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Proportionalities: A Decade of Housing Markets to Subway Stations in Manhattan from 2006 to 2016," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Available:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4836}{\texttt{Link}} ]\space\faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4835}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/gis}{\texttt{Link}} ]\space\faCertificate\space Faculty [ \href{https://www.leahmeisterlin.com/teaching#/gis-2017-2018/}{\texttt{Link}} ]\newline\newline
        % N. Kunz, "Reimaged: John Snow's Cholera Map of 1854, "Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Available:\newline\newline
        % \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/reimagined}{\texttt{Link}} ]\newline\newline
        G. S. Coch, S. Nelsen, \textbf{N. Kunz}, "Seeking Refuge: The Geography of Migrant Deaths Along the US-MX Border," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Availabile:\newline\newline
        \faTrain\space GSAPP [ \href{https://www.arch.columbia.edu/student-work/4895}{\texttt{Link}} ]\space\faMedium\space Medium [ \href{https://medium.com/data-mining-the-city/seeking-refuge-the-geography-of-migrant-deaths-near-the-us-mx-border-b0f8f8be84ec}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Traditional Theory and the Historic Preservation of Singapore in the Period of the 1980's," Grad. Sch. of Arch., Plan., and Pres. (GSAPP), Columbia Univ., New York, NY, 2017. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/singapore}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Health \& Wellness Alliance for Children: Children's Asthma, Healthy Physical Environments, Dallas County, Texas," bcWORKSHOP, Dallas, TX, 2014. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/asthma}{\texttt{Link}} ]\newline\newline
        N. Kunz, "The Bexar Street Corridor: A Century in Development, Dallas, Texas," bcWORKSHOP, Dallas, TX, 2013. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/bexar_present}{\texttt{Link}} ]\space\faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/bexar}{\texttt{Link}} ]\space\faHome\space bc [ \href{https://www.bcworkshop.org/posts/bexar-street-corridor}{\texttt{Link}} ]\space\faVimeo\space Vimeo [ \href{https://vimeo.com/81649797}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Fenway-Kenmore Square: Comprehensive Planning \& Finance, Cambridge, Massachusetts," Grad. Sch. of Design (GSD), Harvard Univ., Cambridge, MA, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/fenway_kenmore}{\texttt{Link}} ]\newline\newline
        % N. Kunz, "Design Representation: Analog Modeling \& Hand Drafting," Grad. Sch. of Design (GSD), Harvard Univ., Cambridge, MA, 2012. [Online]. Availabile:\newline\newline
        % \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/design_rep}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Danelle Plaza: Complete Street Mobility Planning, Tempe, Arizona," Herberger Inst. for Des. and the Art., Arizona State Univ., Tempe, AZ, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/danelle_plaza}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Ascension: Multifamily Mixed-Use Real Estate Development Proposal, Tempe, Arizona," n Creative Studios, Phoenix, AZ, 2012. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/ascension}{\texttt{Link}} ]\newline\newline
        N. Kunz, "Sui Residence: Second Story Architecture Development Proposal, Paradise Valley, Arizona," n Creative Studios, Phoenix, AZ, 2011. [Online]. Availabile:\newline\newline
        \faBook\space Issuu [ \href{https://issuu.com/nickkunz/docs/sui}{\texttt{Link}} ]
\newpage
    \section*{Honors \& Awards}
        \textbf{Distinguished Alumni Award}, Arizona State University | Tempe, AZ\hfill{2016}\newline
        \textbf{Eli Segal AmeriCorps Education Award}, AmeriCorps | Dallas, TX\hfill{2014}\newline
        \textbf{Dingwall Foundation Scholarship}, William Orr Dingwall Foundation | Washington, DC\hfill{2011 - 2012}\newline
        \textbf{Barrett, The Honors College Scholarship}, Arizona State University | Tempe, AZ\hfill{2010 - 2012}\newline
        \textbf{AIERF Undergraduate Scholarship}, Appraisal Institute | Chicago, IL\hfill{2010 - 2011}\newline
        \textbf{Herberger Institute for Design \& the Arts Scholarship}, Arizona State University | Tempe, AZ\hfill{2010}\newline
        \textbf{Study.net Foundation Scholarship}, Study.net | Fort Lauderdale, FL\hfill{2010}\newline
        \textbf{Dean's List} \textit{(4.00/4.00 GPA)}, Arizona State University | Tempe, AZ\hfill{2009 - 2012}
    \section*{Talks, Exhibits \& Presentations}
        \textbf{Urban Planners in Technology}, Alumni Panel, Columbia University | New York, NY\hfill{2021}\newline
        \textbf{Urban Planning Showcase}, End of Year Show, Columbia University | New York, NY\hfill{2019}\newline
        \textbf{The Bexar Street Corridor}, US Congrasswoman Eddie Bernice Johnson's Office | Dallas, TX\hfill{2014}\newline
        \textbf{The Bexar Street Corridor}, TR Hoover Community Development Corporation | Dallas, TX\hfill{2014}\newline
        \textbf{The Bexar Street Corridor}, bcSHOPFRONT Series, bcWORKSHOP| Dallas, TX\hfill{2013}\newline
        \textbf{Realizing Interactive Architecture}, Honors Symposium, Arizona State University | Tempe, AZ\hfill{2012}
    \section*{Mentorship Activities}
        \textbf{Chawner Hurd}, MBA, Business, Columbia University | New York, NY\hfill{2020 - 2021}\newline
        \textit{Military service transition from US Army, 5th Special Forces Group to graduate school.}\newline\newline
        \textbf{Michael Bollinger}, BA, Computer Science, Columbia University | New York, NY\hfill{2019 - 2021}\newline
        \textit{Military service transition from US Army, 75th Ranger Regiment to undergraduate school.}\newline\newline
        \textbf{Daniel Hineline}, BA, Political Science, Columbia University | New York, NY\hfill{2018 - 2021}\newline
        \textit{Military service transition from US Army, 82nd Airborne Division to undergraduate school.}
    \section*{Military Service}
    \subsection*{Assignments}
        \textbf{US Army, 75th Ranger Regiment} | Fort Lewis, WA \hfill{2015 - 2016}\newline
        \textit{Infantry}\newline\newline
        \textbf{US Army, Ranger Training Detachment} | Fort Benning, GA \hfill{2015}\newline
        \textit{Ranger Assessment and Selection Program}\newline\newline
        \textbf{US Army, 1st Special Warfare Training Group} | Fort Bragg, NC \hfill{2014}\newline
        \textit{Special Forces Assessment and Selection}\newline\newline
        \textbf{US Army, 1st Special Warfare Training Group} | Fort Bragg, NC \hfill{2014}\newline
        \textit{Special Forces Preparation and Conditioning}\newline\newline
        \textbf{US Army, 507th Parachute Infantry Regiment} | Fort Benning, GA \hfill{2014}\newline
        \textit{Airborne School}\newline\newline
        \textbf{US Army, 19th Infantry Regiment} | Fort Benning, GA \hfill{2014}\newline
        \textit{Infantry School}
    \subsection*{Decorations}
        \textbf{Expert Badge, Rifle Component Bar}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2016}\newline
        \textbf{Global War on Terrorism Service Medal}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2016}\newline
        \textbf{Driver Badge, Wheeled Vehicle Component Bar}, US Army, 75th Ranger Regiment | Fort Lewis, WA\hfill{2015}\newline
        \textbf{Parachutist Badge, Unit Trimming}, US Army, 507th Parachute Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{Infantry Blue Chord Fourragère}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{National Defense Service Medal}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}\newline
        \textbf{Army Service Ribbon}, US Army, 19th Infantry Regiment | Fort Benning, GA\hfill{2014}
    \section*{Civil Service}
        \textbf{Smithsonian Institution} | Washington, DC \hfill{2020 - 2021}\newline
        \textit{Digital Transcription}\newline\newline
        \textbf{AmeriCorps} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Volunteer in Service to America (VISTA)}\newline\newline
        \textbf{Open Architecture Collaborative} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Non-Profit Architecture \& Planning}\newline\newline
        \textbf{Trinity Park Conservancy} | Dallas, TX \hfill{2013 - 2014}\newline
        \textit{Public Park Conservation}
    \section*{Technical Skills}
    \subsection*{Languages}
        \textbf{Scripting}: Python, Bash\newline
        \textbf{Statistical}: R, Stata\newline
        \textbf{Compiled}: C/C++, Fortran\newline
        \textbf{Database}: SQL, NoSQL\newline
        \textbf{Typesetting}: \LaTeX, Markdown
    \subsection*{Frameworks}
        \textbf{Data Science}: NumPy, SciPy, Pandas, statsmodels, Featuretools, Tidyverse, Dplyr\newline
        \textbf{Visualization}: Matplotlib, Seaborn, Plotly, Processing, Shiny, ggplot\newline
        \textbf{Statistical Learning}: Scikit-Learn, XGBoost, LightGBM, CatBoost\newline
        \textbf{Reinforcement Learning}: OpenAI Baselines, Stable Baselines\newline
        \textbf{Deep Learning}: Pytorch, TensorFlow, ONNX

    \subsection*{Deployment}
        \textbf{DevOps}: Git, Ubuntu, Docker, Kubernetes, CI/CD Pipelines, Pickle\newline
        \textbf{Databases}: SQL Server, PostgreSQL, SQLite, CosmosDB, Blobs\newline
        \textbf{Web Services}: Flask, Gunicorn, Nginx\newline
        \textbf{Web Automation}: Selenium, Puppeteer\newline
        \textbf{Cloud Platforms}: Azure, Azure Gov, AWS\newline
        \textbf{Security}: OWASP ZAP, STIGs
    \subsection*{Software}
        \textbf{Development Environments}: VS, VS Code, RStudio, Jupyter, Spyder\newline
        \textbf{Geographic Information Systems}: ArcGIS, QGIS, OSM, Leaflet, Mapbox\newline
        \textbf{3D Modeling \& Optimization}: Rhino, Grasshopper, SketchUp, AutoCAD, Unity\newline
        \textbf{Design \& Illustration}: Adobe Photoshop, Illustrator, InDesign\newline
        \textbf{Financial Modeling}: Excel, Macros, CoStar\newline
        \textbf{Studio \& Live Audio}: Logic, Protools
    \subsection*{Prototyping}
        \textbf{Sensors \& Hardware}: Arduino, Raspberry Pi, GPU, FPGA\newline
        \textbf{Project Management}: Agile, Scrum, Critical Path\newline
        \textbf{Electrical}: Soldering, Wiring, Safety\newline
        \textbf{Ideation}: Drawing \& Sketching, Storyboarding\newline
        \textbf{Analogs}: Hand Drafting, Physical Modeling, Photography
    \section*{Personal Activities}
    \subsection*{Music \& Live Audio}
        \textbf{Atlas North American Tour} | US \& Canada\hfill{2013}\newline
        The Word Alive \textit{(Fearless Records)}, Co-Tour Manager\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline\newline
        \textbf{Fight the Silence Tour} | US\hfill{2013}\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline
        For Today \textit{(Razor \& Tie Records)}, Guitar Tech\newline\newline
        \textbf{All Stars Tour} | US\hfill{2012}\newline
        The Word Alive \textit{(Fearless Records)}, Guitar Tech\newline
        A Skylit Drive \textit{(Fearless Records)}, Guitar Tech\newline\newline
        \textbf{Van's Warped Tour} | US \& Canada\hfill{2011}\newline
        The Word Alive \textit{(Fearless Records)}, Co-Tour Manager\newline
        Of Mice \& Men \textit{(Rise Records)}, Guitar Tech\newline\newline
        \textbf{Regional Performances} | US\hfill{2011}\newline
        The Rendering \textit{(Authentik Artists)}, Guitar
    \subsection*{Outdoors \& Endurance}
        Running \textit{(Half Marathon, 13.1mi, Marathon, 26.2mi)}\newline
        Cycling \textit{(Century Ride, 100mi)}\newline
        Hiking \textit{(Mt. Rainier, Mt. Olympus, Mt. Denali)}\newline
        Overlanding \textit{(Rubicon Trail, Alaskan Arctic Circle, All 50 States)}\newline
        Snowboarding \textit{(Cascades, Sierra Nevadas, Colorado Plateau, Mississippi River Valley)}\newline
        \mbox{}
        \vfill
        \hfill{}\textit{Updated: Sept. 2021}
\end{document}